### 2016-09-19 Thesis/DCG_sb-wi-thesis-template/intro/UPS.tex
intro complete again

\begin{figure}[p]
	\centering
	\includegraphics[width=\columnwidth]{intro/pag1flagap.png}
	\mycaption{Confirmation of MSpC accuracy by analysis of MS/MS datasets generated with the Universal Proteome Standard 2 (UPS2)}{Affinity purification of 26S proteasomes from \textit{PAG1::PAG1-FLAG pag1-1} plants}
	{\citep{book10} \textbf{(A)} SDS-PAGE analysis of proteins obtained at each affinity purification step.  Total protein extracts from 10 day old wild-type (WT) and \textit{PAG1::PAG1-FLAG pag1-1} plants were incubated with anti-FLAG affinity resin, washed, and competitively eluted with the FLAG peptide. The procedure was performed in the presence or absence of ATP, and the input, unbound, washed and eluted fractions were subjected to SDS-PAGE and the gel stained for protein with silver.  The black arrowhead indicates the PAG1-FLAG protein, while the open arrowhead identifies nitrilase, which is non-specifically enriched during the purification. \textbf{(B)} Immunoblot detection of various 26S proteasome subunits in the affinity-purified preparations shown in A. Subunits tested include the CP subunits PAG1 and PBA1, the RP subunits RPT2, RPN1, RPN5, RPN10 and RPN12a, and the alternate capping particle PA200.  Other proteins tested include the Rubisco small subunit and nitrilase. This figure was modified from reference \citep{book10}.}
	\label{fig:pag1flagap}
\end{figure}

>>>>

\begin{figure}[p]
	\centering
	\includegraphics[width=\columnwidth]{intro/pag1flagap.png}
	\mycaption{Affinity purification of 26S proteasomes from \textit{PAG1::PAG1-FLAG pag1-1} plants}
	{\citep{book10} \textbf{(A)} SDS-PAGE analysis of proteins obtained at each affinity purification step.  Total protein extracts from 10 day old wild-type (WT) and \textit{PAG1::PAG1-FLAG pag1-1} plants were incubated with anti-FLAG affinity resin, washed, and competitively eluted with the FLAG peptide. The procedure was performed in the presence or absence of ATP, and the input, unbound, washed and eluted fractions were subjected to SDS-PAGE and the gel stained for protein with silver.  The black arrowhead indicates the PAG1-FLAG protein, while the open arrowhead identifies nitrilase, which is non-specifically enriched during the purification. \textbf{(B)} Immunoblot detection of various 26S proteasome subunits in the affinity-purified preparations shown in A. Subunits tested include the CP subunits PAG1 and PBA1, the RP subunits RPT2, RPN1, RPN5, RPN10 and RPN12a, and the alternate capping particle PA200.  Other proteins tested include the Rubisco small subunit and nitrilase. This figure was modified from reference \citep{book10}.}
	\label{fig:pag1flagap}
\end{figure}
